---
title: "Homework Data Viz"
author: "Thongpan Win"
date: "2023-05-06"
output: html_document
---

# Hello World
This is markdown language. Today we learn a few topics in R.

- databases
- working with date
- ggplots
- rmarkdown

## Homework

Explore dataframe 'diamond' and create 5 visualizations.

### Chart 1 Range of cut and clarity
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(patchwork)
library(ggplot2)
head(diamonds)
```

Range of carat
```{r}
min(diamonds$carat)
max(diamonds$carat)
carat_h <- diamonds$carat
  h <- hist(carat_h,
  main="Distribution of carat in data set",
  sub="We found a high number of diamonds size from 0-1.5 carats",
  xlab="Carat",
  col="blue",
  xlim=c(0,5.01),
  )
text(h$mids,h$counts,labels=h$counts, adj=c(0.5, -0.5), cex=0.6, col ="red")
print(h)
```

We divided diamonds in to two groups (0-1.5 and 1.51-5.01)
```{r}
library(patchwork)
library(ggplot2)
set.seed(1234)
all <-ggplot(diamonds %>% sample_n(5000), aes(x=carat))+
  geom_histogram(bins=5)

# Filter carat range between 0.2 to 1.5 carat
c1 <-filter(diamonds, between(carat, 0.2,1.5))
set.seed(1234)
ggplot(c1 %>% sample_n(5000), aes(x=carat))+
  geom_histogram(bins=5)
# Filter carat range between 1.51 to 5.01 carat
c2 <-filter(diamonds, between(carat, 1.51,5))
set.seed(1234)
ggplot(c2 %>% sample_n(5000), aes(x=carat))+
  geom_histogram(bins=5)

```

Relationship between carat and price.
```{r}
#all
set.seed(1234)
ggplot(diamonds %>% sample_n(5000), mapping=aes(carat, price, col=cut))+
  geom_boxplot(size=1, alpha=0.5) + 
  theme_minimal()+
  labs(
    title = "Relationship between carat and price",
    x = "Carat ranged 0.2-5 ",
    y = "Price USD",
    subtitle = "We found a positive relationship",
    caption = "Datasource: diamonds ggplot2"
  )

##c1
ggplot(c1 %>% sample_n(5000), mapping=aes(carat, price, col=cut))+
  geom_boxplot(size=1, alpha=0.5) + 
  theme_minimal()+
  labs(
    title = "Relationship between carat and price",
    x = "Carat ranged 0.2-1.5 ",
    y = "Price USD",
    subtitle = "We found a positive relationship",
    caption = "Datasource: diamonds ggplot2"
  )
set.seed(1234)
ggplot(c2 %>% sample_n(5000), mapping=aes(carat, price, col=cut))+
  geom_boxplot(size=1, alpha=0.5) + 
  theme_minimal()+
  labs(
    title = "Relationship between carat and price",
    x = "Carat ranged 1.51-5.01 ",
    y = "Price USD",
    subtitle = "Most Ideal cut were between 1.51 to 5.01 carats",
    caption = "Datasource: diamonds ggplot2"
  )
```

### Chart 3 Relationship between carat and color for each clarity
```{r}
ggplot(c1 %>% sample_n(5000), 
       mapping=aes(color, carat, color=cut))+
  geom_point(size=1, alpha=0.5)+ 
  facet_wrap(~ clarity)+
  theme_minimal()+
  labs(
    title = "Relationship between carat(ranged 0.2 to 1.5) and color",
    x = "color",
    y = "carat",
    subtitle = "We found a positive relationship",
    caption = "Datasource: diamonds ggplot2"
  )
```

### Chart 4 Relationship between carat (0.2-1.5 carat), price, and cut for each clarity.
```{r}
ggplot(c1,
       mapping=aes(carat, price))+
  geom_point(size=0.5, alpha=0.2)+ 
  facet_grid(clarity ~ cut)+
  theme_minimal()+
  labs(
    title = "Relationship between carat(ranged 0.2 to 1.5) and price",
    x = "carat",
    y = "price",
    subtitle = "We found a positive relationship",
    caption = "Datasource: diamonds ggplot2"
  )
```



Comment what did we found?
We found a positive relationship between two variables.

[google](https://www.google.com)
![add new image](plus.unsplash.com)




